### 2024-03-26 content/chapter_4.tex
:construction: Update motivation
:pencil: Update chapter 3

\chapter{RIScatter: Unifying \glsfmtshort{bc} and \glsfmtshort{ris}}

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
	\end{subsection}

@@

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_tags.tex}
				}
			}
			\subfloat[Reflection States\label{fg:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_txs.tex}
				}
			}
			\subfloat[Spreading Factor\label{fg:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_noise.tex}
				}
			}
			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_csi.tex}
				}
			}
			\\
			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_snr_primary.tex}
				}
			}
			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_snr_backscatter.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
		\end{subsubsection}

@@

		\begin{subsubsection}{Number of Transmit Antennas}
			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
		\end{subsubsection}

@@

		\begin{subsubsection}{Primary \gls{snr}}
			\label{sc:primary_snr}
			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
		\end{subsubsection}

>>>>

\chapter{RIScatter: Unifying \glsfmtshort{bc} and \glsfmtshort{ris}}\label{ch:riscatter}

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter trade-off with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
	\end{subsection}

@@

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_tags.tex}
				}
			}
			\subfloat[Reflection States\label{fg:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_txs.tex}
				}
			}
			\subfloat[Spreading Factor\label{fg:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_noise.tex}
				}
			}
			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_csi.tex}
				}
			}
			\\
			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_snr_primary.tex}
				}
			}
			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_snr_backscatter.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter trade-off.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
		\end{subsubsection}

@@

		\begin{subsubsection}{Number of Transmit Antennas}
			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter trade-off.
			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
		\end{subsubsection}

@@

		\begin{subsubsection}{Primary \gls{snr}}
			\label{sc:primary_snr}
			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter trade-off in active-passive coexisting networks.
		\end{subsubsection}

### 2024-03-26 content/chapter_5.tex
:construction: Add motivation
:construction: Update motivation
:pencil: Add wave scattering models
:pencil: Update chapter 3

\chapter{\glsfmtshort{mimo} Channel Shaping using \glsfmtshort{ris}: From Diagonal to Beyond}

@@

\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
	The overall scattering matrix of the \gls{bd}-\gls{ris} is
	\begin{equation}
		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
	\end{equation}
	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
	That is, $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{H}$ and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.

@@

			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.

@@

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
		\end{subsubsection}

@@

		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
		At a transmit power of \qty{10}{dB}, Fig. \subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to 4T4R \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better tradeoff between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.

>>>>

\chapter{Channel Shaping and Interference Alignment using \glsfmtshort{ris}: From Diagonal to Beyond}\label{ch:channel_shaping}

@@

\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
	The overall scattering matrix of the \gls{bd}-\gls{ris} is
	\begin{equation}
		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
	\end{equation}
	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
	That is, $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.

@@

			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a trade-off between the direct-indirect and backward-forward alignments.

@@

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between aligning the two subspaces.
			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
		\end{subsubsection}

@@

		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
		At a transmit power of \qty{10}{dB}, Fig. \subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to 4T4R \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better trade-off between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
	This translates to a wider dynamic range (with better trade-off) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
